\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\date{}

\begin{document}

\subsection{Profiles}\label{profiles}

P1: Reuse components

{[}priority: high{]} {[}\emph{TODO: check: CMDValidate}{]}

A main idea behind the CMD framework is the use of existing components
to reduce the amount of work and to improve the general quality of
profiles by benefiting from existing work of more experienced users.
Therefore it is strongly encouraged to check the existing stock of
profiles and components regarding their usefulness for your specific
needs.

As it is very likely that at least some of the aspects of every resource
type are comparable to other resources (e.g.~standard descriptive
metadata like resource name, license or providing organisation), these
are natural candidates for a successful reuse. A profile that does not
use existing components or that does not make use of any non-inline
components contradicts the general idea of CMDI and is therefore
undesirable. For a fast insight on which components are recommended by
experienced profile designers, these components are included in the
group ``recommended'' and can be displayed in the standard component
registry {[}\emph{TODO}{]}. For a similar reason it is advised to
compare a new design with recommended profiles. (See section
\href{/recommendations/README.md}{Recommendations}.)

P2: One component for one aspect

{[}priority: medium{]}

Different components in a profile should be exclusive concerning their
scope. This means that every relevant aspect of a resource type should
be dealt with in a single (possibly complex) component to avoid semantic
overlaps between different parts of a profile.

P3: Support broad user groups

{[}priority: medium{]}

In large federated research infrastructures, a resource may be relevant
for user groups that were not primarily targeted and that may lack
information about the context in which a resource was originally
created. Therefore every resource description should be self-contained
and all information that may seem to be implicit (like language, age,
size, format or origin of a resource) should be made explicit to
facilitate the use of a resource in new scientific contexts.

P4: Use Documentation

{[}priority: medium{]} {[}\emph{TODO: partially check: CMDValidate}{]}

CMDI allows extensive documentation of every part of a CMD metadata
schema. This also holds for CMD Profiles. It is strongly encouraged to
add a meaningful description to a profile, containing a general
explanation of the purpose of the profile. This description should also
be understandable for users without expert knowledge in the specific
field. Domain-specific terminology may not be suitable for a proper
understanding. In this case a general and a domain specific description
could be helpful. If the profile has a specific relevance for a concrete
scientific domain (like lexicography or phonetics), this information
should be specified for the profile too.

TODO: P5: minimal semantic coverage

{[}priority: medium{]} {[}\emph{TODO: check:CMDValidate}{]}

\emph{A profile should (at least via concept links) cover a, agreed upon
by the CLARIN community, minimal set of concepts, e.g.~language and
license.}

\end{document}
