\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\date{}

\begin{document}

\subsection{How to use this Guide}\label{scope}

Although the guide will express the best practices in strict wording, it
is possible, and sometimes even allowed to break a best practice. To
indicate the impact of breaking a best practice a priority level is
given:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \emph{High priority}: a CMD record not following this best practice
  severely counters the ground principle of CMDI \emph{{[}TODO:
  reference{]}}, e.g.~reusable components with explicit semantics, or
  common best practices for resources on the web, e.g.~URLs should be
  resolvable not dead links \emph{{[}TODO: reference{]}};
\item
  \emph{Medium priority}: default priority of a best practice, which
  means it can be broken if you have good local (technical or
  organizational) reasons to deviate;
\item
  \emph{Low priority}: a CMD record meeting this best practice is better
  adapted to the CLARIN infrastructure, but not following it will not
  have bad consequences.
\end{enumerate}

\begin{longtable}[c]{@{}l@{}}
\toprule
\begin{minipage}[b]{0.07\columnwidth}\raggedright\strut
Note by Menzo
\strut\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
ground principles of CMDI: 1) components, 2) generic as possible
specific as needed (reusable), 3) explicit semantics
\strut\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

Best practices with a \emph{high} priority should be followed. If a best
practice with a medium level priority is not followed the reasons why
should always be documented.

Compliance with some best practices can be (partially) assessed
automatically. CLARIN provides the following tools and services:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  CMDValidator:\footnote{See
    \url{https://github.com/clarin-eric/cmd-validate/releases}} The
  validator for CMD components and profiles is in general used via the
  Component Registry;
\item
  CMDI Instance Validator:\footnote{See
    \url{https://github.com/clarin-eric/cmdi-instance-validator/releases}}
  The corresponding validator for CMD records;
\item
  CLARIN curation module:\footnote{See
    \url{https://clarin.oeaw.ac.at/curate/}} This service provides
  insight into the quality of CMD profiles, records and endpoints, which
  can be accessed directly via their URLs.
\end{enumerate}

The functionalities of the two more low level validators are being
integrated into the CLARIN curation module to provide a single service
for CMD quality assessment \emph{{[}TODO{]}}.

\begin{longtable}[c]{@{}l@{}}
\toprule
Note by Menzo\tabularnewline
\midrule
\endhead
@Matej: is ``are being integrated into'' not a too strong
claim?\tabularnewline
\bottomrule
\end{longtable}

Some best practices have a direct relationship with the CLARIN B Centre
requirements (\href{http://hdl.handle.net/11372/DOC-78}{CE-2013-0095}),
which is indicated next to the priority. A CLARIN B Centre will have to
meet such a requirement and the best practice.

\end{document}
