\section{Optimising for
discoverability}\label{optimising-for-discoverability}

\todo{See
\href{https://www.gitbook.com/book/cmdi-taskforce/cmdi-best-practices/changes/23}{CR
\#23}}

An important motivation for creating and publishing high quality metadata for resources is that doing so can vastly increase the discoverability of these resources. Metadata generally provides information that is not (directly) available from the associated digital object, service, tool or other resource itself, and therefore caters to use cases complementary to \emph{content search}.

Most of the best practices described in this document serve the purpose, either implicitly or explicitly, to improve the discoverability of the described resources. Therefore in general it can be said that following the described best practices as closely as possible is the best way to optimise for discoverability. However in this section we will explicitly assume the perspective of discoverability and focus on a number of salient aspects that either have the potential of strongly affecting discoverability, are a common cause of suboptimal discoverability, or may not be obvious to the average metadata modeller or author.

A few examples of scenarios we consider cases of resource discovery and believe should be recognised and considered in the context of metadata modelling and authoring: \note{sh: ``A few examples of scenarios \textbf{which} we consider {[}\ldots{}{]} are listed below:'';
``Here we list a few examples \ldots{} which \ldots{}''}

\begin{itemize}
\tightlist
\item
  A user visits a \textbf{specific repository} where they may or may not expect to find access to a certain resource, or a resource with certain properties. If successful, the desired resource is provided to the user through the platform that was used to initiate the discovery.
\item
  A user visits a metadata-driven catalogue, search engine or other \textbf{platform that aggregates metadata} from multiple sources, such as the \href{https://www.clarin.eu/vlo}{Virtual Language Observatory}, and browses or queries the indexed records on basis of a more or less specific set of criteria, eventually reaching a location that provides (a path to) access to the actual resource, which may involve one or more intermediate steps including one or more interactions with the `native' repository (see above) that hosts the resource.
\item
  A user performs a search using a \textbf{general purpose search engine} (such as Google) that crawls web pages and other online content, using salient keywords that match the metadata and/or content of the resource. Results that lead the user to the resource may include the repository or another search or aggregation platform.
\item
  A resource is \textbf{referenced} in a paper, in online content such as a website or blog post, or included in a collection that is consumed by a user, and hence discovered. The reference has to be actionable in some way and provide direct or indirect access to the actual resource in order for the discovery process to be considered successful.
\end{itemize}

Metadata creators can choose to optimise for one or more types of discovery scenarios.

\subsection{Metadata formats and
representation} \label{metadata-formats-and-representation}

By design, metadata aggregators such as the VLO have a more or less \textbf{generic search interface and data model}, which means that in most cases they will not be as well suited for searching for resources in a specific context as search platforms tailored to that context. I.e., repositories with a relatively limited scope in terms of content can harness their `knowledge' about the contained information and its shape to provide enhanced means of search, exploration and presentation. In fact, many repository solutions have a data schema (encoded in their database or other data storage facility) that is optimised for these purposes. In those cases, CMDI or for example Dublin Core metadata is often only made available (exported) as `secondary' form of representation. In many cases this is an apt solution, that makes it possible to combine the benefits of specificity and generality. However it is also important that the exported metadata is not merely \emph{available} but actually \textbf{fit for aggregation}, which implies a different context than that of the `native' repository. Factors to keep in mind when designing the export from an internal representation to metadata for harvesting:

\subparagraph{Implicit vs explicit context} \label{implicit-vs-explicit-context}

The meaning of abbreviations and ids or `relative' descriptors (e.g. `Organisation: Linguistics department') might be understood or resolvable within its native context but aggregation will make such context far less obvious or even invisible.

\subparagraph{Custom vocabularies vs broadly adapted vocabularies} \label{custom-vocabularies-vs-broadly-adapted-vocabularies}

Often tailor made vocabularies are used that allow for description and classification of resources with a high level of accuracy and detail. However in an aggregated context, the value of more generic but broadly understood and supported vocabularies becomes apparent. Obviously the information exposed by highly specific vocabularies don't have to be
sacrificed when exporting metadata, but one should consider extending the metadata with additional values from commonly understood vocabularies. For example, your metadata might contain detailed spatial information in the form of geographic coordinates; in that case your repository can probably process this information well but the same cannot be assumed from any aggregator. A good strategy would be to also export one or more levels of corresponding geographical common names (e.g.~country, city).

\subparagraph{Nature of the targeted aggregation
platform(s)} \label{nature-of-the-targeted-aggregation-platforms}

As a metadata provider you will generally know which platform(s) will aggregate your metadata, or else it is likely to be in your interest to cater for one or more highly relevant aggregators, for example popular domain aggregators. Find out which vocabularies are supported by these aggregators, which information gets displayed saliently and how links back to your resources and/or repository are achieved.

\subsection{Metadata completeness and VLO facets} \label{metadata-completeness-and-vlo-facets}

Providing correct and complete metadata improves discoverability. The more information you provide about your resources and their context, the higher the expected recall for queries that match your data. If you are looking for good representation and discoverability through the VLO, pay
attention to its \textbf{facets}, which can be considered one of the main entry points into the data aggregated into the VLO. Ideally \emph{each metadata record} covers as many facets as possible. Furthermore, a number of non-facet fields are displayed prominently in the search results, in particular a record's \textbf{title and description}, as well as licence and availability information. Records that are lacking this essential information not only are harder to find than those which do, but also are less likely to receive a high ranking
in the search results. \note{sh: ``not only are harder to
find \textbf{than} those which do, but \textbf{are also} less likely''}

A repository may simply export its metadata to \textbf{Dublin Core}. This is one of the requirements of OAI-PMH (see
\href{https://www.openarchives.org/OAI/2.0/openarchivesprotocol.2015-01-08.htm\#Record}). However, one has to be aware that the set of attributes included in `pure' Dublin Core does not necessarily allow for complete or semantically unambiguous metadata. If you are looking to tune your metadata to one ore more parts of the CLARIN infrastructure, it's strongly suggested to investigate the option of exporting to a fitting
CMDI profile, or to make your own dedicated profile if no such profile can be found. If this is not an option, you can also consider using the \href{http://www.language-archives.org/OLAC/metadata.html}{OLAC extensions} to enrich your Dublin Core metadata.

Finally, be aware that the VLO, and the CLARIN infrastructure in general, will generally assume that a metadata record is
self-sufficient. This might differ from the way `native' repositories process and present metadata. For example, if the name of the identity of your organisation is not represented in a record, it will also not be associated with the described resources by the VLO. A metadata hierarchy might provide additional context, such as project information, collection details or legal status, but this will not cause this information to be presented in the context of the resource in a clear way unless it is explicitly included in its own metadata record.

To find out how well your metadata record will be represented in the VLO you may consult the \textbf{Metadata Curation Module}.
\note{Alex: Should have a link to the MD Curation Module}
Here, you are able to upload your metadata record, browse through a list of available profiles or upload a profile URL in order to obtain a ``score'' and an overview of facet coverage for the respective profile or file.

\subsection{Values and semantics}\label{values-and-semantics}

[Consider given vocabularies, e.g.~resource type (including links where to find these)]

[Ensure conformity among records of a collection/institution
(e.g.~naming conventions)]

Facet ``collection'': If you are preparing a set of records that belong to one collection, this collection can be specified in the CMDI header in each record and thus made findable via the VLO facet. If so, make sure that the collection is named homogeneously across records so that the collection name will appear only once in the VLO collection facet. [Prefix collection]

[Modeller's responsibility to avoid ambiguities that can't be resolved technically (e.g. \textless{}date\textgreater{} in very generally named branches: date of what (creation/description/submission/modification)?): naming and most importantly concept/context]

[Avoid non-alphanumeric characters in titles
(\href{https://www.gitbook.com/book/cmdi-taskforce/cmdi-best-practices/discussions/19}{Discussion
\#19})]

\subsection{Links and context}\label{links-and-context}

[Importance of landing page]
