\section{How to use this Guide}

Although the guide will express the best practices in strict wording, it
is possible, and sometimes even allowed to break a best practice. To
indicate the impact of breaking a best practice a priority level is
given:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \emph{High priority}: a CMD record not following this best practice
  severely counters the ground principle of CMDI \emph{{[}TODO:
  reference{]}}, e.g.~reusable components with explicit semantics, or
  common best practices for resources on the web, e.g.~URLs should be
  resolvable not dead links \emph{{[}TODO: reference{]}};
\item
  \emph{Medium priority}: default priority of a best practice, which
  means it can be broken if you have good local (technical or
  organizational) reasons to deviate;
\item
  \emph{Low priority}: a CMD record meeting this best practice is better
  adapted to the CLARIN infrastructure, but not following it will not
  have bad consequences.
\end{enumerate}

\note{Menzo: ground principles of CMDI: 1) components, 2) generic as possible specific as needed (reusable), 3) explicit semantics}
Best practices with a \emph{high} priority should be followed. If a best
practice with a medium level priority is not followed the reasons why
should always be documented.

Compliance with some best practices can be (partially) assessed
automatically. CLARIN provides the following tools and services:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  CMDValidator:\footnote{See
    \url{https://github.com/clarin-eric/cmd-validate/releases}} The
  validator for CMD components and profiles is in general used via the
  Component Registry;
\item
  CMDI Instance Validator:\footnote{See
    \url{https://github.com/clarin-eric/cmdi-instance-validator/releases}}
  The corresponding validator for CMD records;
\item
  CLARIN curation module:\footnote{See
    \url{https://clarin.oeaw.ac.at/curate/}} This service provides
  insight into the quality of CMD profiles, records and endpoints, which
  can be accessed directly via their URLs.
\end{enumerate}

The functionalities of the two more low level validators are being
integrated into the CLARIN curation module to provide a single service
for CMD quality assessment \emph{{[}TODO{]}}.
\note{Menzo: @Matej: is ``are being integrated into'' not a too strong
claim?}

Some best practices have a direct relationship with the CLARIN B Centre
requirements (\href{http://hdl.handle.net/11372/DOC-78}{CE-2013-0095}),
which is indicated next to the priority. A CLARIN B Centre will have to
meet such a requirement and the best practice.
