\subsection{The envelope}\label{the-envelope}

\subsubsection{Header}\label{header}

E1: Include a MdSelfLink

{[}priority: high{]} {[}CLARIN Centre B requirement: 6.7{]} {[}check:
CMDI Instance Validator{]}

Include a MdSelfLink that resolves to the CMD record hosted at the
CLARIN Centre. Including the MdSelfLink is a requirement for CLARIN B
Centres (see
\href{http://hdl.handle.net/1839/00-DOCS.CLARIN.EU-78}{CE-2013-0095}
section 6 sub-requirement 7) as is the support of content negotiation
for the MdSelfLink (see
\href{http://hdl.handle.net/1839/00-DOCS.CLARIN.EU-78}{CE-2013-0095}
section 7), this allows both human and machines to see/retrieve the
record in its context. The MdSelfLink is also important in the
reconstruction of a CMD record (collection) hierarchy (see below).

E2: The MdSelfLink should be a Persistent Identifier (PID)

{[}priority: medium{]} {[}CLARIN B Centre requirement: 6.7{]}
{[}\emph{TODO: check: CMDI Instance Validator}{]}

By giving a CMD record a PID and including it in the MdSelfLink it
becomes possible for tools that present the records to the user to
provide them with a persistent link suitable as a bookmark that will
stand the test of time. This is another requirement for CLARIN B Centres
(see
\href{http://hdl.handle.net/1839/00-DOCS.CLARIN.EU-78}{CE-2013-0095}
section 6 sub-requirement 7).

E3: Include a MdCollectionDisplayName

{[}priority: medium{]} {[}\emph{TODO: check: CMDI Instance Validator}{]}

The MdCollectionDisplayName allows grouping of records, e.g.~for display
or search, without the need to access or even the existence of an
explicit CMD collection record. Including the CLARIN Centre name and a
collection name enables users to quickly assess the provenance, scope
and context of an individual record. Generic tools, like the VLO, use
this information to put a record in context. Use a consistent collection
name across records that belong to the same collection and should be
presented as such.

E4: Include a matching MdProfile

{[}priority: high{]} {[}CLARIN B Centre requirement: 6.9.a{]} {[}check:
CMDI Instance Validator{]}

The MdProfile contains the unique identifier of the used profile in the
Component Registry. This element is mandatory in CMDI 1.2 but optional
in CMDI 1.1. However, it should always be included and it should match
with the XSD (see
\href{/authoring_component_metadata_records/general_xml.md\#x1}{X1}).
While the reference to the XSD is an absolute URI the MdProfile just
needs to contain the identifier, e.g.
\texttt{clarin.eu:cr1:p\_1361876010680}.

\subsubsection{Resource Proxies}\label{resource-proxies}

E5: There should be at least one resource proxy

{[}priority: high{]} {[}check: CMDI Instance Validator{]}

A CMD record describes one or more (collections of) resources. These
(collections of) resources, where the minimum is one resource or
collection, should be linked to the CMD record via a resource proxy.
This allows central tools, like the VLO, to show the user the resources
related to the metadata. It is also technically possible, but not
preferred (see
\href{/authoring_component_metadata_records/the_component_section.md\#cs2}{CS2}),
to include the resource URLs/PIDs in the component section, however they
should always be available as resource proxies.

E6: The URI of a resource proxy should be absolute and resolvable

{[}priority: high{]} {[}\emph{TODO: check: CMDI Instance Validator}{]}

An absolute URI should be used as the value of ResourceRef. This is
certainly true for published CMD records. Internally a centre can use
relative URLs, but care should be taken to make them absolute when
publishing them to the infrastructure.

Also the URI of a resource proxy should be resolvable, i.e.~the resource
should be available at that location. However, it might be a protected
and thus (shibboleth-based) authentication might be required.

\paragraph{Metadata}\label{metadata}

E7: ``Metadata'' type resource proxies should refer to a CMD record

{[}priority: high{]} {[}\emph{TODO: check: CMDI Instance Validator}{]}

The only metadata format used by CLARIN is CMD, so a metadata resource
proxy should refer to a CMD record as should be indicated by the MIME
type ``application/x-cmdi+xml''.

E8: ``Metadata'' type resource proxies should use PIDs

{[}priority: medium{]} {[}CLARIN B Centre requirement: 6.7{]}
{[}\emph{TODO: check: CMDI Instance Validator}{]}

A CMD record should be available via a PID (with(out) a part identifier)
(see
\protect\hyperlink{e2-the-mdselflink-should-be-a-persistent-identifier-pid}{E2}
and \href{http://hdl.handle.net/1839/00-DOCS.CLARIN.EU-78}{CE-2013-0095}
section 6 sub-requirement 8). General tools, like the VLO, use these
links among CMD records to reconstruct the collection hierarchy. To be
able to do so it is important that the PID used in the metadata resource
proxy of a collection record and the MdSelfLink in the referenced CMD
record are equal.

\paragraph{Resource}\label{resource}

\begin{longtable}[c]{@{}l@{}}
\toprule
\begin{minipage}[b]{0.05\columnwidth}\raggedright\strut
TODO
\strut\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.05\columnwidth}\raggedright\strut
Is there an indication of the mime type? Does it match the actual mime
type of the response obtained from the resource location?
\strut\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[c]{@{}l@{}}
\toprule
TODO\tabularnewline
\midrule
\endhead
The use of format variants.\tabularnewline
\bottomrule
\end{longtable}

E9: Specify the MIME type of a resource

{[}priority: high{]} {[}\emph{TODO: check: CMDI Instance Validator}{]}

Give the MIME type (a.k.a. media type) of the resource. This enables
general tools, like the Language Resource Switchboard, to direct users
to tools and/or services that can process or display this type of
resources. Sometimes the MIME type is too coarse, e.g., for TEI
resources, in that case a format variant can be added to fine tune the
type. However, the format variant should come from a controlled
vocabulary. The MIME type is also part of the HTTP response when
resolving the ResourceProxy reference, which should match the MIME type
specified.

E10: ``Resource'' type resource proxies should use PIDs

{[}priority: medium{]} {[}CLARIN B Centre requirement: 7{]}
{[}\emph{TODO: check: CMDI Instance Validator}{]}

A resource should be available via a PID (with or without a part
identifier) (see
\href{http://hdl.handle.net/1839/00-DOCS.CLARIN.EU-78}{CE-2013-0095}
section 7).

\paragraph{LandingPage}\label{landingpage}

E11: Provide no more than one LandingPage

{[}priority: medium{]} {[}CLARIN B Centre requirement: 6.8{]}
{[}\emph{TODO: check: CMDI Instance Validator}{]}

The landing page ResourceProxy takes the user to a page within the web
interface of the repository in which the CMD record resides. The landing
page usually serves as a starting point for more detailed scrutiny of
the metadata, e.g.~by displaying core information up front, while
providing links to the finer details. There might be multiple
interfaces, but general tools, like the VLO, do not have information to
choose which one is appropriate. To prevent a possible random selection
of the landing page resource proxies, which could provide a confusing
user experience, provide no more than one landing page.

\paragraph{SearchPage}\label{searchpage}

E12: Provide no more than one one SearchPage

{[}priority: medium{]} {[}\emph{TODO: check: CMDI Instance Validator}{]}

The search page resource proxy takes the user to a place where the
record/collection/repository can be searched. There might be multiple
search interfaces, but general tools, like the VLO, do not have
information to choose which one is appropriate. To prevent a possible
random selection of the search page resource proxies, which could
provide a confusing user experience, provide no more than one search
page.

\paragraph{SearchService}\label{searchservice}

E13: Provide no more than one SearchService

{[}priority: medium{]} {[}TODO: check: CMDI Instance Validator{]}

The search service resource proxy enables tools to search the
record/collection/repository. There might be multiple search services,
but general tools, like the VLO or the FCS aggregator, do not have
information to choose which one is appropriate. To prevent a possible
random selection of the search service resource proxies or the use of
overlapping services where resources might be returned more than once,
which could provide a confusing user experience, provide no more than
one search service.

E14: A SearchService should support the FCS specification

{[}priority: medium{]} {[}CLARIN B Centre requirement: 8{]}
{[}\emph{TODO: check: CMDI Instance Validator}{]}

The only search API supported by CLARIN is the one specified in the FCS
specification.\footnote{See
  \url{https://www.clarin.eu/content/federated-content-search-clarin-fcs}}
Any search service included in a CMD record should thus support this
specification.

\subsubsection{Journal Proxies}\label{journal-proxies}

Not used by CLARIN.

\subsubsection{Resource Relations}\label{resource-relations}

\begin{itemize}
\item
  {[} {]} See \url{https://trac.clarin.eu/wiki/VLO-Taskforce/Relations}
\item
  {[} {]} See
  \url{https://trac.clarin.eu/wiki/CMDI\%201.2/Resource\%20proxies/ResourceRelation}
\end{itemize}

E15: Use ResourceRelation to express any significant binary
relationships among resources listed in ResourceProxyList

{[}priority: low{]}

Each ResourceRelation instance must reference the two related resources
and be defined by a relationship type. Relationship types should be
assigned a concept link describing its meaning, see also C12. When
deciding which relationships should be explicitly represented, consider
relations which may be useful in several usecases. Some examples of
typical or relevant relationships between two resources R1 and R2
include: \emph{R1 annotates R2}, \emph{R1 transcribes R2}, \emph{R1 is
parallel to R2} (e.g.~in a parallel corpus listing each language file as
separate resources), and others.

E16: Add roles to both relationship participants when considered useful

{[}priority: medium{]} {[}\emph{TODO: check: CMDI Instance Validator}{]}

To convey the full nature of the relationship between two resources, it
is sometimes desirable to assign roles to the related parties. If so, it
is best practice to assign roles to both parties (not only one).
Moreover, each role should be assigned a concept link to express its
meaning, see also
\href{/modelling_component_metadata/components.md\#c14}{C14}.

E17: Use ResourceProxy to express partitive relationships between the
described resource as a whole and its constituent resources.

{[}priority: medium{]}

If your resource is decomposed into separate parts, each child resource
should be listed as a ResourceProxy instance in the ResourceProxyList.
For any child resource having its own CMD record, the corresponding
ResourceProxy should be of type Metadata, and its ResourceRef should be
set to MdSelfLink of its CMD record. See also
\protect\hyperlink{e5-there-should-be-at-least-one-resource-proxy}{E5}-\protect\hyperlink{e8-metadata-type-resource-proxies-should-use-pids}{E8}.

This top-down approach is the preferred way of describing resource
hierarchies, as it is generally supported throughout the core CLARIN
infrastructure. See also
\href{/common_approachesproblems/granularity.md}{Granularity}.

E18: IsPartOf may be used to express a partitive relation between the
described resource as a whole and a larger resource or collection

{[}priority: low{]} {[}TODO: check: \emph{CMDI Instance Validator}{]}

This is a bottom-up method of describing resource hierarchies, and
constitutes an alternative or additional approach to that described in
\protect\hyperlink{e17-use-resourceproxy-to-express-partitive-relationships-between-the-described-resource-as-a-whole-and-its-constituent-resources}{E17}.
So far, IsPartOf is not widely used nor well supported by the CLARIN
infrastructure, hence the
\protect\hyperlink{e17-use-resourceproxy-to-express-partitive-relationships-between-the-described-resource-as-a-whole-and-its-constituent-resources}{E17}
approach should be preferred whenever feasible. See also
\href{/common_approachesproblems/granularity.md}{Granularity}.

E19. Use the right mechanism to define relations in your metadata

{[}priority: high{]}

Note that ResourceRelation is strictly connected to ResourceProxy in the
sense that both resources related by ResourceRelation must be instances
of ResourceProxy. Any other relationships, e.g.

\begin{itemize}
\tightlist
\item
  between ResourceProxy instances and the described resource as a whole
  or other (external) resources,
\item
  non-partitive relations between the described resource as a whole and
  other (external) resources, or
\item
  relations between ResourceProxy instances and other entities mentioned
  in the CMD record, e.g.~persons or institutions
\end{itemize}

must be expressed using suitable components and elements available in
the chosen profile, if any. If no applicable mechanism is available in
the current profile, consider extending it with additional components,
for instance some dedicated relationship component.

\subsubsection{Foreign attributes}\label{foreign-attributes}

TODO: E20: Delete foreign attributes before providing

{[}priority: low{]} {[}TODO: check: CMDI Instance Validator{]}

See \href{/authoring_component_metadata_records/general_xml.md\#x2}{X2}.
